Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-05 testbed.tex
More fixes to testbed intro

To get started, we first need to install an \ac{OS} on the
Raspberry Pis. We will use Raspbian linux~\cite{raspbian}

We will use a desktop that has linux installed to download,
configure, and write the image to the memory cards.
%We have decided to use a linux desktop machine to create a
%common image of Raspbian Linux that can be used in any of the Raspberry Pis.

@@

We have decided to go with Raspbian linux~\cite{raspbian} and
to install it on memory cards.

@@

There exists a number of ways to setup a testbed

with multiple devices. We
have decided on a very simple approach of simply instal

-
- Download image (wget)
- Update/Modify image (chroot)
- Burn image
- Bang! linux is running
-

Open a terminal, and then...

hashmark (\#) means to perform operation as root, dollar (\$) means to perform operation as user

The first thing we need to do is to download the linux installation file.
For Raspbian, this is available at \url{http://downloads.raspberrypi.org}.

Raspbian is made available in two bundles. Raspbian and Raspbian lite.
The difference between the two is that Raspbian contains a pre-installed desktop
environment, and Raspbian lite is by default only accessable through a shell. 
They will both also be remotely accessible using \ac{SSH}.

Our testbed does not have monitors so we will install Raspbian lite.
A desktop environment can always be installed manually in case that will be
desired sometime in the future.

Below is a procedure of how we setup the \ac{Raspi}s in our testbed. We
have decided a simple setup where each \ac{Raspi} is equipped with a
memory card that contains a slightly customized Raspbian lite image with
identical settings.

The reason this can be done easily is because the official Raspbian lite image
that we will download simply conntains a complete linux installation that are
packaged in an image rather than written to a harddrive, memory card, or usb
pen.

The overall steps to customize the official Raspbian lite image are listed below:
\begin{enumerate}
    \item Download Raspbian lite
    \item Alter Raspbian lite. E.g. browse, modify, add, and delete files
        in the official Raspbian lite image
    \item Change root. I.e. change root filesystem into the Raspbian lite
        image to update and install software packages
    \item Write image to memory cards
\end{enumerate}

>>>>

To get started, we first need to install an \ac{OS} on the
\ac{Raspi}s. We will use Raspbian linux~\cite{raspbian}

We will be using a \ac{PC} running a Debian-based linux distribution
to setup a customized Raspbian linux image that can be written to
a memory card and work in any \ac{Raspi} version 1 or 2.
%We will use a desktop that has linux installed to download,
%configure, and write the image to the memory cards.
%We have decided to use a linux desktop machine to create a
%common image of Raspbian Linux that can be used in any of the Raspberry Pis.

@@

%We have decided to go with Raspbian linux~\cite{raspbian} and
%to install it on memory cards.

@@

%There exists a number of ways to setup a testbed
%
%with multiple devices. We
%have decided on a very simple approach of simply instal

%-
%- Download image (wget)
%- Update/Modify image (chroot)
%- Burn image
%- Bang! linux is running
%-

%Open a terminal, and then...

\textbf{hashmark (\#) means to perform operation as root, dollar (\$) means
to perform operation as user}

%The first thing we need to do is to download the linux installation file.
%For Raspbian, this is available at \url{http://downloads.raspberrypi.org}.

Raspbian is made available in two bundles. Raspbian and Raspbian lite.
The difference between the two is that Raspbian contains a pre-installed desktop
environment, and Raspbian lite is by default only accessible through a 
command shell. 
Both Raspbian and Raspbian lite will both by default be remotely
accessible using \ac{SSH}. \ac{SSH} provides the means to remotely
connect to another machine through a command shell. In fact it is the successor
of \ac{Telnet} that has been designed with network security in mind.

Our testbed does not have monitors so we will install Raspbian lite.
A desktop environment can be installed using Raspbian's package manager
(apt-get) in case a desktop environment will be desired sometime in the future.

Below is the procedure we did to setup the \ac{Raspi}s in our testbed. We
have performed a simple setup where each \ac{Raspi} is equipped with a
memory card that contains a slightly customized Raspbian lite image with
identical settings.

%The reason this can be done easily is because the official Raspbian lite image
%that we will download simply conntains a complete linux installation that are
%packaged in an image rather than written to a harddrive, memory card, or usb
%pen.

The overall procedure to customize the official Raspbian lite image
are:
\begin{enumerate}
    \item Download Raspbian lite
    \item Alter Raspbian lite. E.g. browse, modify, add, and delete files
        in the official Raspbian lite image
    \item Change root. I.e. change root filesystem into the Raspbian lite
        image to update and install software packages
    \item Write image to memory cards
\end{enumerate}
